Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

Another closely related query is the {\em reverse-containment query}, which, given an interval $q = [z_1, z_2]$, finds all the intervals of $S$ that contain $q$ (rather than ``being contained by $q$''). Again, we can store $S$ in a PST using $O(|S|)$ space such that any such query can be answered in $O(\log |S| + K)$ time, where $K$ is the number of intervals reported. In general, an interval $[x, y]$ contains another $[z_1, z_2]$ if and only if the point $(x, y)$ falls in the 3-sided rectangle $(-\infty, z_1] \times [z_2, \infty)$. Thus, we create from $S$ a point set $P = \set{(x, y) \mid [x, y] \in S}$ and store $P$ in a PST. Given an interval $q = [z_1, z_2]$, we use the PST to find all the points in $P$ covered by $(-\infty, z_1] \times [z_2, \infty)$ and, for each such point $(x, y)$, report $[x, y]$.

>>>>

Another closely related query is the {\em reverse-containment query}, which, given an interval $q = [z_1, z_2]$, finds all the intervals of $S$ that contain $q$ (rather than ``being contained by $q$''). Again, we can store $S$ in a PST of $O(|S|)$ space that answers such a query in $O(\log |S| + K)$ time, where $K$ is the number of intervals reported. In general, an interval $[x, y]$ contains another $[z_1, z_2]$ if and only if the point $(x, y)$ falls in the 3-sided rectangle $(-\infty, z_1] \times [z_2, \infty)$. Thus, we create from $S$ a point set $P = \set{(x, y) \mid [x, y] \in S}$ and store $P$ in a PST. Given an interval $q = [z_1, z_2]$, we use the PST to find all the points in $P$ covered by $(-\infty, z_1] \times [z_2, \infty)$ and, for each such point $(x, y)$, report $[x, y]$.
